\EL{Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques}

### 2020-02-28 jfm/draft_p2_jfm.tex
Add references suggested by referees

%
In fluid turbulence, rare-event sampling has been approached mainly from the perspective of simplified dynamics such as the one-dimensional Burgers' equation with a stochastic forcing \citep{bec_burgers_2007}. In this case, dynamics can be sampled by using a Markov chain Monte-Carlo algorithm \citep{duben_monte_2008,mesterhazy2011anomalous,mesterhazy2013lattice} that provides a framework for rare-event sampling.
%
An alternative approach is based on instantons \citep{gurarie_instantons_1996,grafke2015instanton} and applies to stochastically driven systems in the limit of weak noise.
Instantons refer to the most probable trajectories in phase space that achieve a given rare event (in the limit of weak noise). Suitable numerical schemes can be used to evaluate instantons as well as the related probabilities of rare events \citep{chernykh_large_2001,grafke_instanton_2013,grigorio_instantons_2017,laurie2015computation,bouchet2014langevin}.
An example is the investigation of the physics of rogue waves~\citep{dematteis2018rogue,dematteis2019experimental}.
%
However, a drawback of the aforementioned approaches is their limitation to simple and stochastically driven dynamics.
%
%
%
Here, a more general approach is considered for complex, possibly deterministic, dynamical systems.
It is based on sampling algorithms relying on \emph{selection rules} applied to an ensemble of trajectories of the system. 
%, and is designed to sample rare events of some observable with a higher frequency.
%    
%
Even though such ideas date back to the early 1950s, they have received growing interest over the last twenty years with successful applications in various domains such as chemistry \citep{van_erp_elaborating_2005,escobedo_transition_2009,teo_adaptive_2016}, biophysics \citep{huber_weighted-ensemble_1996,zuckerman2017weighted,bolhuis2005kinetic}, nuclear physics \citep{louvin2017}, nonlinear dynamical systems \citep{tailleur_probing_2007} and communication networks simulation \citep{villen-altamirano_restart:_1994}.
More importantly, such algorithms have been shown to be useful for the study of rare events in simple deterministic dynamics~\citep{wouters2016rare}.
%
%
\EL{Certainly, an original contribution of our study is to test the application of rare-event sampling algorithms in the context of far-from-equilibrium dynamics with an irreducible very large number of degrees of freedom. 
%
Two algorithms that are a priori suitable for such dynamics are considered, namely, the Adaptive Multilevel Splitting (AMS) algorithm \citep{cerou_adaptive_2007} and the Giardina-Kurchan-Tailleur-Lecomte (GKTL) algorithm \citep{giardina_direct_2006}.}
%

%
% MOVED TO SECTION 4
%
%The \acl{ams} algorithm \citep{cerou_adaptive_2007} builds on previous ideas about splitting approaches \citep{KahnHarris1951,glasserman_look_1998,glasserman_multilevel_1999} -- a detailed description will be given later.  
%In recent years, it has allowed for the computation of rare events in problems involving a large number of degrees of freedom such as molecular dynamics simulations \citep{aristoff_adaptive_2015,teo_adaptive_2016}. The first use of the \ac{ams} algorithms for more complex dynamics, for instance stochastic partial differential equations was for the computation of rare trajectories in the Allen-Cahn equations \citep{rolland_computing_2016}. More recently \EL{it} has been applied to rare events in stochastic models of wall-turbulence \citep{rolland_extremely_2018} and atmospheric dynamics \citep{bouchet2019rare}.
%
%During the last decade, the main theoretical framework for the study of rare events in statistical physics has been the theory of large deviations \citep{touchette_large_2009}.
%Alongside numerical methods have been developed to sample rare events \citep{DelMoralBook}. 
%Among them the \ac{gktl} algorithm \citep{giardina_direct_2006} is particularly suited for (chaotic) dynamical systems \citep{giardina_simulating_2011,Laffargue_2013}.
%%
%{Recently the \ac{gktl} algorithm has allowed to successfully perform the numerical simulation of extreme heat waves in a simplified modelling of the atmosphere \citep{ragone_computation_2018}. 
%	This achievement represents a significant leap in the applicability of rare-event sampling to complex dynamical systems. Along the same line, \EL{rare-event sampling algorithms are here applied outside of traditional applications by considering fluid-structure interaction in a turbulent flow}.}
%

@@

During the last decade, the main theoretical framework for the study of rare events in statistical physics has been the theory of large deviations \citep{touchette_large_2009}.
Alongside, numerical methods have been developed to sample rare events \citep{DelMoralBook}. 
Among them the \ac{gktl} algorithm \citep{giardina_direct_2006} is particularly suitable for \EL{estimating the probability of observables which are temporal integrals over a very long period \citep{giardina_simulating_2011,Laffargue_2013}.
%
Recently the \ac{gktl} algorithm has proven to be extremely efficient to simulate extreme heat waves in a comprehensive climate model \citep{ragone_computation_2018}, with a gain of a factor 100 to 1000 for the computation time.}
This achievement already represents a significant leap in the applicability of rare-event sampling to complex dynamical systems. 
\EL{The aim of this part of our work is to test rare-event algorithms for fluid-structure interaction in a turbulent flow, which is a completely new field of application.}

>>>>

In fluid turbulence, rare-event sampling has been approached mainly from the perspective of simplified dynamics such as the one-dimensional Burgers' equation with a stochastic forcing \citep{bec_burgers_2007}. In this case, dynamics can be sampled by using a Markov chain Monte-Carlo algorithm \citep{duben_monte_2008,mesterhazy2011anomalous,mesterhazy2013lattice} that provides a framework for rare-event sampling.
An alternative approach is based on instantons \citep{gurarie_instantons_1996,grafke2015instanton} and applies to stochastically driven systems in the limit of weak noise.
Instantons refer to the most probable trajectories in phase space that achieve a given rare event (in the limit of weak noise). Suitable numerical schemes can be used to evaluate instantons as well as the related probabilities of rare events \citep{chernykh_large_2001,grafke_instanton_2013,grigorio_instantons_2017,laurie2015computation,bouchet2014langevin}.
An example is the investigation of the physics of rogue waves~\citep{dematteis2018rogue,dematteis2019experimental}.
However, a drawback of the aforementioned approaches is their limitation to simple and stochastically driven dynamics.
Here, a more general approach is considered for complex, possibly deterministic, dynamical systems.
It is based on sampling algorithms relying on \emph{selection rules} applied to an ensemble of trajectories of the system. 
%, and is designed to sample rare events of some observable with a higher frequency.
Even though such ideas date back to the early 1950s, they have received growing interest over the last twenty years with successful applications in various domains such as chemistry \citep{van_erp_elaborating_2005,escobedo_transition_2009,teo_adaptive_2016}, biophysics \citep{huber_weighted-ensemble_1996,zuckerman2017weighted,bolhuis2005kinetic}, nuclear physics \citep{louvin2017}, nonlinear dynamical systems \citep{tailleur_probing_2007} and communication networks simulation \citep{villen-altamirano_restart:_1994}.
More importantly, such algorithms have been shown to be useful for the study of rare events in simple deterministic dynamics~\citep{wouters2016rare}.
\EL{Certainly, an original contribution of our study is to test the application of rare-event sampling algorithms in the context of far-from-equilibrium dynamics with an irreducible very large number of degrees of freedom. 
Two algorithms that are a priori suitable for such dynamics are considered, namely, the Adaptive Multilevel Splitting (AMS) algorithm \citep{cerou_adaptive_2007} and the Giardina-Kurchan-Tailleur-Lecomte (GKTL) algorithm \citep{giardina_direct_2006}.}
\EL{Another problem related to rare events is the estimation of parameters or statistics from a limited number of samples.  Several authors have proposed original strategies  \citep{Mohamad-ws,Blonigan-ws} such as sequential sampling. These approaches and rare event algorithms could also be considered for applications in wave-structure problems, ship motion and load acting on offshore platforms \citep{belenky-ws}.}
% MOVED TO SECTION 4
%The \acl{ams} algorithm \citep{cerou_adaptive_2007} builds on previous ideas about splitting approaches \citep{KahnHarris1951,glasserman_look_1998,glasserman_multilevel_1999} -- a detailed description will be given later.  
%In recent years, it has allowed for the computation of rare events in problems involving a large number of degrees of freedom such as molecular dynamics simulations \citep{aristoff_adaptive_2015,teo_adaptive_2016}. The first use of the \ac{ams} algorithms for more complex dynamics, for instance stochastic partial differential equations was for the computation of rare trajectories in the Allen-Cahn equations \citep{rolland_computing_2016}. More recently \EL{it} has been applied to rare events in stochastic models of wall-turbulence \citep{rolland_extremely_2018} and atmospheric dynamics \citep{bouchet2019rare}.
%During the last decade, the main theoretical framework for the study of rare events in statistical physics has been the theory of large deviations \citep{touchette_large_2009}.
%Alongside numerical methods have been developed to sample rare events \citep{DelMoralBook}. 
%Among them the \ac{gktl} algorithm \citep{giardina_direct_2006} is particularly suited for (chaotic) dynamical systems \citep{giardina_simulating_2011,Laffargue_2013}.
%{Recently the \ac{gktl} algorithm has allowed to successfully perform the numerical simulation of extreme heat waves in a simplified modelling of the atmosphere \citep{ragone_computation_2018}. 
%	This achievement represents a significant leap in the applicability of rare-event sampling to complex dynamical systems. Along the same line, \EL{rare-event sampling algorithms are here applied outside of traditional applications by considering fluid-structure interaction in a turbulent flow}.}

@@

During the last decade, the main theoretical framework for the study of rare events in statistical physics has been the theory of large deviations \citep{touchette_large_2009}.
Alongside, numerical methods have been developed to sample rare events \citep{DelMoralBook}. 
Among them the \ac{gktl} algorithm \citep{giardina_direct_2006} is particularly suitable for \EL{estimating the probability of observables which are temporal integrals over a very long period \citep{giardina_simulating_2011,Laffargue_2013}.
%
Recently the \ac{gktl} algorithm has proven to be extremely efficient to simulate extreme heat waves in a comprehensive climate model \citep{ragone_computation_2018}, with a gain of a factor 100 to 1000 for the computation time.}
This achievement already represents a significant leap in the applicability of rare-event sampling to complex dynamical systems. 
\EL{The aim of this part of our work is to test rare-event algorithms for fluid-structure interaction in a turbulent flow, which is an unexplored area of application.}
